---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# ukboundaries

The goal of ukboundaries is to ease access to official geographic UK data.
As some in the Free and Open Source Software for Geospatial community (FOSS4G) would say:
"geo for all"!

This data is provided under the terms of the Open Government Licence.
See https://www.ons.gov.uk/methodology/geography/licences for further details.

## Installation

You can install ukboundaries from github with:

```{r gh-installation, eval=FALSE}
# install.packages("devtools")
devtools::install_github("robinlovelace/ukboundaries")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(ukboundaries)
plot(msoa2011_vsimple)
```

## Bash code

Here are a few bash commands I used to rename the package with minimal effort:

```bash
# rename - replace ukborders with ukboundaries:
grep -rl ukborders | xargs sed -i 's/ukborders/ukboundaries/g'
# move data already downloaded but don't 'clobber' existing files:
mv -nv ../ukborders/* ./
# clean repo
git clean -f
```
